---
title: "vignette-625"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette-625}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(cortest625)
```

Start with two equal numerical vectors
```{r}
set.seed(18465)
x <- rnorm(50)
y <- rnorm(50)

cortest625(x, y) #Default is Pearson
cor(x, y)

cortest625(x, y, method = "kendall")
cor(x, y, method = "kendall")

cortest625(x, y, method = "spearman")
cor(x, y, method = "spearman")
```

Using cortest625 with data from mtcars dataset
```{r}
cortest625(mtcars$disp, mtcars$hp) #Pearson is the default
cortest625(mtcars$disp, mtcars$hp, method = "spearman")
cortest625(mtcars$disp, mtcars$hp, method = "kendall")
```

Checking median speed of cor() vs cortest625() via Pearson Correlation Coefficient
```{r}
set.seed(21)
x <- rnorm(50)
y <- rnorm(50)

#Pearson Benchmark
pearson_bench = bench::mark(
  cor(x, y, method = "pearson"),
  cortest625(x, y, method = "pearson")
)
print(pearson_bench$median)
```

Plotting cortest625() performance vs cor() performance (Pearson)
```{r, echo=FALSE}
plot(pearson_bench)
```

Checking median speed of cor() vs cortest625() via Spearman Rank Correlation
```{r, echo = FALSE}
#Spearman Benchmark
spearman_bench = bench::mark(
  cor(x, y, method = "spearman"),
  cortest625(x, y, method = "spearman")
)
print(spearman_bench$median)
```

Plotting cortest625() performance vs cor() performance (Spearman Rank Correlation)
```{r, echo = FALSE}
plot(spearman_bench)
```

Checking median speed of cor() vs cortest625() via Kenall Rank Correlation
```{r, echo = FALSE}
#Kendall Benchmark
kendall_bench = bench::mark(
  cor(x, y, method = "kendall"),
  cortest625(x, y, method = "kendall")
)
print(kendall_bench$median)
```

Plotting cortest625() performance vs cor() performance (Kendall Rank Correlation)
```{r, echo = FALSE}
plot(kendall_bench)
```

Using all.equal to prove equivalence
```{r}
set.seed(185)
x <- rnorm(100)
y <- rnorm(100)

#Showing Spearman is Equal
all.equal(
  cor(x, y, method = "spearman"),
  cortest625(x, y, method = "spearman")
)

#Showing Pearson is Equal
all.equal(
  cor(x, y, method = "pearson"),
  cortest625(x, y, method = "pearson")
)

#Showing Kendall is Equal
all.equal(
  cor(x, y, method = "kendall"),
  cortest625(x, y, method = "kendall")
)
```

